Seasonality in governing upper-ocean dynamics at submesoscales

### 2016-06-07 writeup/rocha_etal.tex
Minor fixes on intro/abs

\begin{abstract}
    Two new high-resolution numerical simulations with embedded tides suggest a
    strong modulation in the governing near-surface dynamics at submesoscales
    (roughly 10-100 km). Consistent with recent studies, deep late Winter mixed layers
    are prone to baroclinic instabilities and submesoscale turbulence
    prevails in wintertime. Inertia-gravity waves, on the other hand, are enhanced near
    the surface when the upper ocean in strongly stratified. Hence, in summertime,
    inertia-gravity waves strongly dominate the surface kinetic energy and
    sea-surface height variance at submesoscales.
\end{abstract}

@@

Inertia-gravity waves, on the other hand, peak in late Summer/early Fall,
when the upper ocean is strongly stratified. Thus there exists a
strong seasonal modulation in the dominant upper-ocean submesoscale dynamics:
submesoscale turbulence dominates the upper-ocean dynamics in late Winter/early Spring,
whereas quasi-linear inertia-gravity waves prevail in late Summer/early Fall.
Because submesoscale turbulence is significantly diminished in late Summer/early Fall,
the present results suggest that inertia-gravity waves account for most of the
summertime submesoscale SSH variability.

>>>>

\begin{abstract}
    Two new high-resolution numerical simulations with embedded tides suggest a
    strong modulation in the governing near-surface dynamics at submesoscales
    (roughly 10-100 km). Consistent with recent studies, deep late Winter mixed layers
    are prone to baroclinic instabilities and submesoscale turbulence
    prevails in late Winter/early Spring. Inertia-gravity waves, on the other hand, are enhanced near
    the surface when the upper ocean in strongly stratified. As a consequence of
    reduction of submesoscale turbulence and enhancement of intertia-gravity waves,
    the latter strongly dominate the submesoscale surface kinetic energy and
    sea-surface height variance in late Summer/early Fall.
\end{abstract}

@@

Inertia-gravity waves, on the other hand, peak in late Summer/early Fall,
when the upper ocean is strongly stratified. Thus there exists a
strong seasonal modulation in the dominant upper-ocean submesoscale dynamics:
submesoscale turbulence dominates the upper-ocean dynamics in late Winter/early Spring,
whereas quasi-linear inertia-gravity waves prevail in late Summer/early Fall.
Because submesoscale turbulence is severely diminished in late Summer/early Fall,
the present results suggest that inertia-gravity waves account for most of the
summertime submesoscale SSH variability.
